---
title: "Predicting from API"
format: html
---

```{r setup}
options(paged.print=FALSE)
```

In final step of the previous notebook we wrapped a **plumber** API around our fitted model that is pinned to Connect.  In this notebook, we show how to make predictions on new data using that API.

In order to do this we will need to do two preliminary steps in Connect:

1. Change the access setting of our deployed API.
2. Change the vanity URL of our deployed API.

## Loading Packages

Let's begin by loading the packages that we will need.
```{r}
#| message: false
library(tidyverse)
library(tidymodels)
library(vetiver)
library(pins)
library(plumber)
```

## Grabbing New Data for Making Predictions

Next, let's grab some new data that we will make predictions for.
```{r}
#| message: false
df_new_data <- read_csv("./data/student-loan-new.csv")
df_new_data
```

## Pointing to API 

At this point we will create a `vetiver_endpoint` object by using the `vetiver_endpoint()` function, which we orient to the `predict` endpoint of our API.
```{r}
endpoint <- vetiver_endpoint("https://colorado.posit.co/rsc/student-loan-api/predict")
endpoint
```


## Making Predictions

Now we can use the base R `predict()` function to make predictions by feeding it the `endpoint` object and the new data.
```{r}
predict(endpoint, df_new_data)
```















































































































































































